The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-27 src/ms.tex
first commit: IDE section outline

>>>>

\begin{itemize}
    \item Overview of Moore support for IDE programs, Astropy philosophy for selecting such works % Need help from CoCo or finance team to write
    \item Astropy participation in NSBP and SACNAS % Lia can write with help of summaries in astropy-project repo
    \item Funded IDE proposal: Outreachy % Some one from outreachy? Brigitta?
    \item Funded IDE proposal: WoCCode % Lia write
    \item NumFOCUS ``Contributor Diversification \& Retention'' (CDR) participation from Astropy % Lia and Adrian co-write?
\end{itemize}
